Revisiting the Classics: Online RL in the Programmable Data-Plane

### 2021-04-20 paper/paper.tex
Time/throughput table.
Latency-focussed plots?

\usepackage[british]{babel}
\usepackage{csquotes}

@@

@@

@@

@@

>>>>

\usepackage[british]{babel}
\usepackage{csquotes}
\usepackage{pifont}

@@

\makeatletter\let\expandableinput\@@input\makeatother
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

@@

?? Mention that you compute action, send action, AND THEN compute update exactly as in that one paper to reduce latency

@@

\section{Potential Integrations}

\subsection{DDoS Defence}
?? Link to my own work
?? Explain how every part may be substituted
?? Bump-in-the-wire at edge nodes.

\subsection{Something host-specific?}
Accelerate something at an end-host...

@@

\subsection{Experimental Setup}

\section{Results}

\begin{table}
	\caption{Throughput and per-item compute time for an RL agent with/without policy learning. State$\rightarrow$action latency equals the offline completion cost. TODO: compare to host machine? Put completion times first? Put multi first?}
	\resizebox{\linewidth}{!}{
		\expandableinput ../tables/build/latency-tput
	}
\end{table}

\begin{figure}
	\resizebox{1.0\linewidth}{!}{
		\includegraphics{../plots/build/rl-perf-tester/work-strat-32bit}
	}
	\caption{?? Choice of work strategy is pretty important I guess}
\end{figure}

\begin{figure}
	\resizebox{1.0\linewidth}{!}{
		\includegraphics{../plots/build/rl-perf-tester/vary-work}
	}
	\caption{?? Max Parallelisation. ?? Bitdepth affects independent cores more.}
\end{figure}

\begin{figure}
	\resizebox{1.0\linewidth}{!}{
		\includegraphics{../plots/build/rl-perf-tester/vary-core}
	}
	\caption{?? Max-size work (129 work-items). ?? Need to dedicate 3 worker to beat independent cores. ?? Sharper perf increase when new physical core added. ?? up to 31 due to master thread.}
\end{figure}
